Likelihood free inference with measurements of galaxy clustering, group richness, and number denisty

### 2015-10-20 halo/text/abc.tex
edited abstract

>>>>

The Halo Occupation Distribution (HOD) model is a powerful prescription of how galaxies populate 
dark matter halos that has had much success in reproducing large scale galaxy clustering and understanding
galaxy evolution within the context of the halo model. Constraints on the parameters of the HOD model have 
so far been imposed using the standard practice of Bayesian inference with likelihood estimation that 
assumes a functional (often times Gaussian) form of the likelihood. Likelihood free inference methods such 
as the Approximate Bayesian Computation (ABC) makes Bayesian inference possible without ever having to calculate the likelihood.

In this work, we present ABC in the context of constraining the parameters of the HOD model. For a mock 
galaxy catalog with known HOD parameters, we use ABC on measurements of a set of observables generated
through HALOTOOLs, a publicly available ..., to infer tight constraints that reproduce the known HOD paramters. 
Since ABC does not require computing the likelihood, we include observables beyond galaxy clustering such as 
the galaxy number density and the galaxy group richness, for which accurately constructing a likelihood is intractable. 
We demonstrate that adding these measurements to our set of observables leads to stronger constraints on the HOD parameters, 
specifically the ones that govern the satellite galaxy population. Moreover, the constraints we infer that 
reproduce the known HOD parameters illustrate the success of ABC in the context of constraining HOD parameters.

We further extend our ABC method with the above set of observables to constrain HOD parameters for the Sloan 
Digital Sky Survey Data Release 7 observed galaxy catalog. The constraints we find on the HOD parameters are consistent with 
(or stronger than) previous constraints in the literature. (Ultimately include more interesting results).
